Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-13 documents/TriangleScenarioArXiv/ts.tex
Added more discussion of preliminary research

    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measurement setting variables are absent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we discuss in detail in \cref{sec:fritz_distribution}. Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the Triangle structure.
    % \comment[E]{Revisions processed up to here thusfar.}

    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}) --- a novel tool for solving causal inference problems. Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints. Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.

    It is worth noting that a number of causal compatibility inequalities for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality for a series of causal structures with $n \in \N$ variables where at most $c \in \N$ share a common ancestor. The Triangle structure is a special case with $c = 2$, $n = 3$. Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations. Most recently, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-classical does not exist in the Triangle structure for \textit{two-outcome} measurements. Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than $2$ outcomes in at least one variable. Moreover we take these observations as motivation to explore incompatibility in Triangle structure for a larger cardinalities.

    In conclusion, the Triangle structure is a causal structure whose non-classicality remains an open problem. The Triangle structure is a desirable case study because there is a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility. This failure represents a gap in our understanding of quantum non-classicality, where recent developments (namely the Inflation Technique) have made partial progress. This document expands on our understanding of non-classicality in the Triangle structure and also our understanding on how to find inequalities using the Inflation Technique for interesting causal structures in general.

@@

    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures. The remainder of this paper focuses on our advancement toward solving Fritz's Problem. \Cref{sec:conclusions} proposes three refinements of Fritz's Problem which are to be labeled \ref{r:1},\ref{r:2} and \ref{r:3} respectively. Specifically, \ref{r:1} embodies the degree in which the results of \cref{sec:found_inequalities} solve Fritz's problem while \ref{r:2} and \ref{r:3} characterize interpretations of Fritz's Problem that remain partially solved.

    \section{Triangle structure Inequalities}
    \label{sec:found_inequalities}

@@

    The second inequality in consideration is the \textit{symmetric} inequality $I\tsb{SymmetricWeb}$. This inequality was able to achieve a greater relative violation than $I\tsb{Web}$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$. Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution. However, this result is far more surprising. Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well. If it were not, one could construct a distribution that violates $I\tsb{SymmetricWeb}$ further by symmetrizing $\prob[\fritz]$ (\cref{fig:symmetrized_fritz}) by normalizing over all possible permutations of $A,B,C$. This distribution is also non-classical with relative violation $V_F = 3$. As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}. Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.

@@

    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum accessible distributions. This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution. In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{0}
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
    \end{enumerate}

>>>>

    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measurement setting variables are absent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we discuss in detail in \cref{sec:fritz_distribution}. Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classicality in the Triangle structure~\cite{Fritz_2012}.
    % \comment[E]{Revisions processed up to here thusfar.}

    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}) --- a novel tool for solving causal inference problems. Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum-inaccessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints. Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.

    It is worth noting that a number of causal compatibility inequalities for the Triangle structure have been derived in previous works. For example, \citet{Steudel_2010} derived an inequality for a series of causal structures with $n \in \N$ variables where at most $c \in \N$ share a common ancestor. The Triangle structure is a special case with $c = 2$, $n = 3$. Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations. Most recently, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}. \Cref{sec:preliminary_research} outlines our initial attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible. The subsequent failure of these approaches will motivate the remainder of this work.

    In conclusion, the Triangle structure is a desirable case study because there exists a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility. This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.

@@

    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to rigorously compare the qualitative features of differing non-classical distributions on differing causal structures (such as the Bell and Triangle structures). The remainder of this paper focuses on our advancement toward solving Fritz's Problem. \Cref{sec:conclusions} concludes by outlining our resolution to Fritz's problem and mentioning areas for future research.

    \section{Preliminary Research}
    \label{sec:preliminary_research}

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-classicality does not exist in the Triangle structure for \textit{two-outcome} measurements. Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than two outcomes in at least one variable. Pursuant to this conjecture, this work expands the search for quantum-accessible incompatibility in Triangle structure by increasing the cardinality of outcomes.

    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly suggests the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution. The Inflation Technique has been shown to completely solve the classical causal inference problem~\cite{Navascues_2017} --- indicating that these undiscovered inequalities can be generated using sufficiently complex inflations. The 37 inequalities in~\cite{Inflation} were derived using the Spiral inflation (\cref{fig:spiral_inflation}) and their failure motivated us to consider larger inflations such as those in \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}.

    These incipient insights were sufficient for focusing the search for new inequalities to $4$-outcomes which are violated by the Fritz distribution. \Cref{sec:found_inequalities} expands on our understanding of non-classicality in the Triangle structure by reporting the discovery of these inequalities which admit quantum-accessible violations. As a by-product, this research supports illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.

    \section{Triangle Structure Inequalities}
    \label{sec:found_inequalities}

@@

    The second inequality in consideration is the \textit{symmetric} inequality $I\tsb{SymmetricWeb}$. This inequality was able to achieve a greater relative violation than $I\tsb{Web}$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$. Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution. However, this result is far more surprising. Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well. If it were not, one could construct a distribution that violates $I\tsb{SymmetricWeb}$ further by symmetrizing $\prob[\fritz]$ (\cref{fig:symmetrized_fritz}) by normalizing over all possible permutations of $A,B,C$. This distribution is also non-classical with relative violation $V_F = 3$. As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}. Therefore we conclude that the space of quantum-accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.

@@

    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions. This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution. In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
    \begin{enumerate}[label=\textbf{R.\arabic*}]
        \setcounter{enumi}{0}
        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
    \end{enumerate}
